Goes Here

### 2012-07-30 paper.tex
fix 'f'

reducer can be dened in two dierent ways. First, a reduction model can be explicitly specied by an expert, for
example, by dening structures of base materials and rules how dierent base materials can be combined together.

>>>>

reducer can be defined in two different ways. First, a reduction model can be explicitly specified by an expert, for
example, by defining structures of base materials and rules how different base materials can be combined together.
